Adaptive Safe Strong Screening for Efficient Lasso-Type Problems Optimization over the Solution Path

### 2020-09-19 main.tex
Update plots

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[ruled,vlined, linesnumbered]{algorithm2e}
\usepackage[english]{babel}
\usepackage[nottoc]{tocbibind}
\usepackage{color}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{float}
\newtheorem{theorem}{Theorem}[section]
\bibliographystyle{abbrvnat}
% Custom commands / shortcuts
\providecommand{\sign}{\textrm{sign}}
\providecommand{\note}[1]{\textcolor{red}{#1}}
\providecommand{\lam}{\lambda}

\title{Adaptive Safe Strong Screening for Efficient Lasso-Type
Problems Optimization over the Solution Path}
\author{Chuyi Wang\\Department of Statistics and Actuarial Sciences\\University of Iowa
  \and
  Patrick Breheny\\Department of Biostatistics\\University of Iowa}
\date{}

\begin{document}

\maketitle

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale = 0.5]{plots/batchsizes.png}    \caption{Proportion of features rejected by screening rules vs index of $\lambda$-values for different update delay.}
    \label{fig:3.4.1}
\end{figure}

>>>>

@@

\begin{figure}[H]
    \centering
    \includegraphics[scale = 0.6]{plots/batchsizes.pdf}    \caption{Proportion of features rejected by screening rules vs index of $\lambda$-values for different update delay.}
    \label{fig:3.4.1}
\end{figure}
